Probabilities of polar alignment in circumbinary disks

### 2024-12-15 src/tex/ms.tex
Revise the grav inst. consequences

\subsubsection{Consequences for $f_\text{polar}$}
The above discussion places an upper limit on what values of $j$ are physical in a given system. As a consequence, a high-$j$ disk is either unstable or highly radially extended. A radially extended disk is more likely to break, effectively lowering the value of $j$. This process is highly dependent on the parameters of a particular system, but it would seem that there is a general preference for small $j$ by means of gravitational instability and disk breaking.

It is worth noting, however that gravitational instability is inherently a local process. An instability in a single region of the disk will not cause the whole disk to become unstable.

>>>>

\subsubsection{Consequences for $f_\text{polar}$}
The above discussion places an upper limit on what values of $j$ are physical in a given system. As a consequence, a high-$j$ disk is either unstable or highly radially extended. A radially extended disk is more likely to break, effectively lowering the value of $j$. This process is highly dependent on the parameters of a particular system, but it would seem that there is a general preference for small $j$ by means of gravitational instability and disk breaking. It may be then, that the distributions of the polar fraction presented in this paper when $j=0$ are the most realistic.
